### 2024-08-26 paper.tex
more of intro

\section{Introduction}
We will review the definition of a Springer fiber and define, for a nilpotent \(Y \in \gl_m\), the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
For every \(n\) and every nilpotent \(Y \in \gl_m\), we will find the irreducible components of the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
Finally, we will use our results about Springer fibers at \(n\)-Slodowy slices to find the irreducible components of some other variety (which probably needs a name), and show that they all have the same dimension.
\par Let \(\mathfrak{g} = \gl_m \times \gl_{m + n}\), with \(n > 0\).
The nilpotent cone in \(\mathfrak{g}\) is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), where \(\mathcal{N}_m\) and \(\mathcal{N}_{m + n}\) are the nilpotent cones in \(\gl_m\) and \(\gl_{m + n}\) respectively.
Let \(\mathcal{B}_m\) and \(\mathcal{B}_{m + n}\) be the varieties of Borel subalgebras of \(\gl_m\) and \(\gl_n\) respectively.
The variety of Borel subalgebras of \(\mathcal{N}\) is \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\).
Let
\[\widetilde{\mathcal{N}} := \{(\mathfrak{b}, n) \in \mathcal{B} \times \mathcal{N} : n \in \mathfrak{b}\} = \]
\[\{(\mathfrak{b}_m, \mathfrak{b}_{m + n}, n_m, n_{m + n}) \in \mathcal{B}_m \times \mathcal{B}_{m + n} \times \mathcal{N}_m \times \mathcal{N}_{m + n} : n_m \in \mathfrak{b}_m, n_{m + n} \in \mathfrak{b}_{m + n}\}.\]
We have a map \(\widetilde{\mathcal{N}} \to \mathcal{N} \hookrightarrow \mathfrak{g}\) given by the Springer resolution.
\par Let \((e, h, f)\) be the principal \(\spl_2\)-triple in \(\gl_n\).
We have an embedding \(\gl_n \hookrightarrow \gl_m \times \gl_n \hookrightarrow \gl_{m + n}\).
Let \((E, H, F)\) be the \(\spl_2\)-triple in \(\gl_{m + n}\) which is the image of \((e, h, f)\) via this embedding.
Let \(S\) be the Slodowy slice \(F + \mathfrak{z}_{\gl_m}(E)\).
We have a map \(\gl_{m + n} \to \gl_m\) given by coordinate projection.
Restricting to \(S\), we obtain \(f_1 : S \to \gl_m\).
(It turns out that this map is surjective.)
Then, we obtain \(p_1 : S \to \mathfrak{g}\) by \(x \mapsto (x, f_1(x))\).
Taking the map \(p_1 : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
\par In this paper we will study \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
The first few sections will be finding what it looks like (in particular, what are the elements of \(S\) which project to nilpotent elements of \(\mathfrak{g}\)), and then we will find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).

@@

\section{Linear Algebra Facts}
In this section we prove linear algebra facts that will be useful later.
A reader uninterested in their verification may wish to read the theorem statements and skip ahead to the next section.

>>>>

\section{Introduction}
We will review the definition of a Springer fiber and define, for a nilpotent \(Y \in \gl_m\), the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
For every \(n\) and every nilpotent \(Y \in \gl_m\), we will find the irreducible components of the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
Finally, we will use our results about Springer fibers at \(n\)-Slodowy slices to find the irreducible components of some other variety (which probably needs a name), and show that they all have the same dimension.
\par Let \(\mathfrak{g} = \gl_m \times \gl_{m + n}\), with \(n > 0\).
The nilpotent cone in \(\mathfrak{g}\) is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), where \(\mathcal{N}_m\) and \(\mathcal{N}_{m + n}\) are the nilpotent cones in \(\gl_m\) and \(\gl_{m + n}\) respectively.
Let \(\mathcal{B}_m\) and \(\mathcal{B}_{m + n}\) be the varieties of Borel subalgebras of \(\gl_m\) and \(\gl_n\) respectively.
The variety of Borel subalgebras of \(\mathcal{N}\) is \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\).
Let
\[\widetilde{\mathcal{N}} := \{(\mathfrak{b}, n) \in \mathcal{B} \times \mathcal{N} : n \in \mathfrak{b}\} = \]
\[\{(\mathfrak{b}_m, \mathfrak{b}_{m + n}, n_m, n_{m + n}) \in \mathcal{B}_m \times \mathcal{B}_{m + n} \times \mathcal{N}_m \times \mathcal{N}_{m + n} : n_m \in \mathfrak{b}_m, n_{m + n} \in \mathfrak{b}_{m + n}\}.\]
We have a map \(\widetilde{\mathcal{N}} \to \mathcal{N} \hookrightarrow \mathfrak{g}\) given by the Springer resolution.
\par Let \((e, h, f)\) be the principal \(\spl_2\)-triple in \(\gl_n\).
We have an embedding \(\gl_n \hookrightarrow \gl_m \times \gl_n \hookrightarrow \gl_{m + n}\).
Let \((E, H, F)\) be the \(\spl_2\)-triple in \(\gl_{m + n}\) which is the image of \((e, h, f)\) via this embedding.
Let \(S\) be the Slodowy slice \(F + \mathfrak{z}_{\gl_m}(E)\).
We have a map \(\gl_{m + n} \to \gl_m\) given by coordinate projection.
Restricting to \(S\), we obtain \(f_1 : S \to \gl_m\).
(It turns out that this map is surjective.)
Then, we obtain \(p_1 : S \to \mathfrak{g}\) by \(x \mapsto (x, f_1(x))\).
Taking the map \(p_1 : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
\par In this paper we will study \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
The first few sections will be finding what it looks like (in particular, what are the elements of \(S\) which project to nilpotent elements of \(\mathfrak{g}\)), and then we will find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
\par As a step towards studying \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we consider the map \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \gl_m\) given by taking the map to \(\mathfrak{g}\) and then projecting to \(\gl_m\).
The main section of this paper will study the fibers of this map.
Given \(X \in \mathcal{N}_m \subseteq \gl_m\), we call the fiber at \(X\) the \emph{\(n\)-Slodowy-slice Springer fiber at \(X\)}.

@@

\section{Linear Algebra Facts}
In this section we prove linear algebra facts that will be used later.
They are proved in this section to avoid interrupting the flow of the remainder of the paper.
